% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

\begin{center}
I would like to dedicate this paper to Mum, Dad, Vivien, Viviana, and Jorden.\\
\end{center}

The formatting of this report was done with Krishna Kumar's Cambridge University Engineering Department PhD thesis 
LaTeX template, and with reference to a Microsoft Word template provided by Dr. Simon Kent. 
The implementation of this project was done with many open-source dependencies.
For the exhaustive list of these external packages used please go to Appendix B.\\

Thanks must be given to my supervisor, Dr. Brijesh Dongol, my second marker, Dr. Mark Perry, 
and to the other tutees in the same supervisory group, for their support and 
formative feedback throughout this project. 
I would also like to thank my coursemates and friends for their support throughout this year.\\

\begin{center}
\section*{Declaration}
\end{center}
\vspace{1cm}
I hereby declare that except where specific reference is made to the work of 
others, the contents of this dissertation are original and have not been 
submitted in whole or in part for consideration for any other degree or 
qualification in this, or any other university. This dissertation is my own 
work and contains nothing which is the outcome of work done in collaboration 
with others, except as specified in the text and Acknowledgements.

\begin{flushright}
Tsz Yiu Lam

4th April 2018
\end{flushright}
\vspace{1cm}
\begin{center}
Word count: 11378 words in main text, excluding appendixes
\end{center}
\end{acknowledgements}
